---
title: "multifractal"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{multifractal}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

## Overview

This is an improved package for multifractal detrended fluctuation (MF-DFA) and surroagte analysis (IAAFT, IAAWT). It allows to enhance the robustness and reliability of classic MF-DFA via overlapping windows. It further enables to test the significance of multifractality via IAAFT surrogates.

## Installation

```{r, eval=FALSE}
devtools::install_github("wol-fi/multifractal")

```

## Usage

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The below example illustrates a multifractal analysis of the S&P 500 stock market index (daily, 1992-2022). The example dataset comes with the package (source: Yahoo finance).

```{r}
library(multifractal)

## preparation:
# load the example dataset 'sp500' and calculate daily log-returns
p <- sp500
r <- diff(log(p$Adj.Close)) 
```

### multifractal analysis

```{r, fig.height = 5, fig.width = 7}
# estimate the statistics
mdl <- mfdfa(r, overlap=T)

## plot the output
plot(mdl, newindow=F)
```

Interpretation:

-   *upper-left:* Fluctuation plot. The slopes of the lines represent the Hurst exponents (one line per moment q). If the lines are parallel then the series is monofractal (e.g., classic Brownian motion), otherwise multifractal.
-   *upper-right:* Multifractal spectrum. The wider, the stronger the degree of multifractality and non-linear auto-correlation. Hölder exponents are abbreviated by \\alpha.
-   *lower-left:* generalized Hurst exponents. Would be approximately flat if monofractal.
-   *lower-right:* Scaling function. Is linear if monofractal, otherwise convex.

##### Extract Persistence and Multifractal Strength

```{r}
stats <- print(mdl)
```

##### Test Significance

```{r}
sig <- significance(mdl, size=10, pval=0.1)

```

##### Compute the Temporal Return Persistence

```{r, fig.height = 5, fig.width = 7}
Ht <- localH(mdl)
plot(Ht, dates=p$Date[-1])
```
